A finite-state morphological transducer for Kyrgyz

### 2012-03-21 paper/paper.tex
moar fixy

The paper is split into five main parts. First a background section gives some details about Kyrgyz and the toolkit used. Subsequent sections describe the tagset and individual issues encountered with the morphotactics and the morphophonology. Finally, some evaluation results are given and future work outlined.

@@

%FIXME: new stuff
That the precision is so high is not surprising: the transducer is rule-based and the test set is the corrected output of the analyser.  In order to get a more accurate figure for precision, it would be necessary to have several linguists review the set.
Our evaluation of the transducer brought to light some systematic ways that we could improve the transducer.

@@

Low precision was due largely to incorrect stem categorisation.  Proofing our stem categorisation would increase precision significantly.  Besides this, several issues with the transducer were brought to light.  One such issue is that mono-syllabic verbs ending in vowels
(e.g., [же] \eng{eat}, [жуу] \eng{wash}, [оо] \eng{tilt})
do not take a gerund/infinitive in -/Uː/, but are only used with the morphologically, semantically, and syntactically similar -/(I)ш/ suffix.  To prevent these forms from being output, a different version of the current verbal continuation lexica should be made to capture the morphological difference---i.e., forms of these verbs that are marked as \texttt{<ger>} should be output with the -/(I)ш/ suffix instead of the -/Uː/ suffix.

>>>>

The paper is split into five main parts. First a background section gives some details about Kyrgyz and the toolkit used.  Subsequent sections describe individual issues encountered with the morphotactics and the morphophonology.  Finally, some evaluation results are given and future work outlined.

@@

%FIXME: new stuff
That the precision is so high is not surprising: the transducer is rule-based and the test set is the corrected output of the analyser.  In order to get a more accurate figure for precision, it would be necessary to have several linguists review the gold standard.

Our evaluation of the transducer brought to light some systematic ways that we could improve the transducer.

@@

Low precision was due largely to incorrect stem categorisation.  Proofing our stem categorisation would increase precision significantly.  Besides this, several issues with the transducer were brought to light.  One such issue is that mono-syllabic verbs ending in vowels
(e.g., [же] \eng{eat}, [жуу] \eng{wash}, [оо] \eng{tilt})
do not take a gerund/infinitive in -/{\qipa Uː}/, but are only used with the morphologically, semantically, and syntactically similar -/(I)ш/ suffix.  To prevent these forms from being output, a different version of the current verbal continuation lexicon should be made to capture the morphological difference---i.e., forms of these verbs that are marked as \texttt{<ger>} should be output with the -/(I)ш/ suffix instead of the -/{\qipa Uː}/ suffix, and analysed likewise.
